Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2022-03-25 response1_BMB.tex
response tag cleanup
1st revision, done

% JD try to write text
\com 1 {\it The main surprising results about the possibility of R0 increasing with increased testing intensity or decreasing with increased delays seem particularly intertwined with the behavior displayed by individuals who are waiting for their test results. In particular, having long delays can make versions of the model with high $\theta\_w$ effectively treat these waiting individuals into a partially socially-distanced or quarantined compartment, while, in versions in which waiting individuals do not change their behavior, increased asymptomatic testing can provide extra time to miss new infectious. This connection between behavior of waiting and confirmed individuals and how testing impacts R0 makes me curious about a few aspects of combining testing with social distancing.

@@

\res 1 We now talk more generally about cautious behavior of people waiting (and cite Muller and Muller 2021 on this topic) in our discussion. 
% {reviewer1:com1 in the manuscript_BMB.tex}

@@

\res 2 This is a good point. We now discuss possible interactions between epidemiological status (as reflected in a more complex model) and testing in the Discussion as a possible future investigation.
% JD try to write text
% {search for reviewer1:com2 in the manuscript_BMB.tex}

@@

\res 3
We now have added a line in the manuscript to describe the parameters involved in the DFE before Equation (4).
% {search for reviewer1:com3 in the manuscript_BMB.tex}

@@

\res 4
We have added a line in the manuscript in Section A.4 of the appendix to clarify the fact that Eq. 27 is a direct result of differentiating $\Delta$ in Eq.7 with respect to $w_{IS}$.
% {search for reviewer1:com4 in the manuscript_BMB.tex}

@@

\res 1
We now have added a line in the manuscript (the first paragraph of the Discussion section) to clarify what we mean by the term ``caricature''. 
% {search for reviewer2:com1 in the manuscript_BMB.tex}

@@

\res 2
We have added some lines to the discussion section of the manuscript to include some potential future work.
% { search for reviewer2:com2 in the manuscript_BMB.tex}

>>>>

\com 1 {\it The main surprising results about the possibility of R0 increasing with increased testing intensity or decreasing with increased delays seem particularly intertwined with the behavior displayed by individuals who are waiting for their test results. In particular, having long delays can make versions of the model with high $\theta\_w$ effectively treat these waiting individuals into a partially socially-distanced or quarantined compartment, while, in versions in which waiting individuals do not change their behavior, increased asymptomatic testing can provide extra time to miss new infectious. This connection between behavior of waiting and confirmed individuals and how testing impacts R0 makes me curious about a few aspects of combining testing with social distancing.

@@

\res 1 We now talk more generally about cautious behavior of people waiting (and cite Muller and Muller 2021 on this topic) in our discussion. (See l. 224ff: ``This finding does, however, suggest ...'')
% {reviewer1:com1 in the manuscript_BMB.tex}

@@

\res 2 This is a good point. We now discuss possible interactions between epidemiological status (as reflected in a more complex model) and testing in the Discussion as a possible future investigation. (See l. 265ff: ``This development would also allow ...'')
% {search for reviewer1:com2 in the manuscript_BMB.tex}

@@

\res 3
We now have added a line in the manuscript to describe the parameters involved in the DFE before Equation (4). (See l. 112ff: ``The DFE depends on ...'')
% {search for reviewer1:com3 in the manuscript_BMB.tex}

@@

\res 4
We have added a line in the manuscript in Section A.4 of the appendix to clarify the fact that Eq. 27 is a direct result of differentiating $\Delta$ in Eq.7 with respect to $w_{IS}$. (See Sec A.4, l. 461ff: ``Using the expression for the ...'')
% {search for reviewer1:com4 in the manuscript_BMB.tex}

@@

\res 1
We now have added some lines in the manuscript (the first paragraph of the Discussion section) to clarify what we mean by the term ``caricature''. (see l. 188ff: ``further, our model ignores ...'')
% {search for reviewer2:com1 in the manuscript_BMB.tex}

@@

\res 2
We have added some lines to the discussion section of the manuscript to include some potential future work. (See l. 224ff: ``This finding does, however, suggest ...'')
% { search for reviewer2:com2 in the manuscript_BMB.tex}
